To Do List

### 2018-09-24 ToDo.Rmd
added todo
completed tasks

+ split feature list into distance then counts
* run mlr/lasso without distances to compare with mourad
* find out how to obtain consensus tree from random forest
+ do we need distance?
+ look at models with just counts vs just distance; compare

>>>>

+ split feature list into distance then counts
+ run mlr/lasso without distances to compare with mourad
* find out how to obtain consensus tree from random forest
+ do we need distance?
+ look at models with just counts vs just distance; compare

+ compare between mourad model and our pipeline at each step (full data vs balanced; distance vs no distance features)
   - lasso to lasso
   - mlr to mlr
